---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
# knitr::opts_chunk$set(
#   collapse = TRUE,
#   comment = "#>",
#   fig.path = "man/figures/README-",
#   out.width = "100%"
# )
```

# figpatch

<!-- badges: start -->
<!-- badges: end -->

The goal of figpatch is to create an easy way to incorporate external figures
and images into figures assembled with
[{patchwork}](https://patchwork.data-imaginist.com/).

## Installation

<!-- You can install the released version of figpatch from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("figpatch") -->
<!-- ``` -->

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("BradyAJohnston/figpatch")
```
## Example

```{r example}
library(figpatch)
library(ggplot2)
library(patchwork)
```

To use images inside of a patchwork object, they need to be converted to a 
`{ggplot}` object via `fig()`. Once converted, you can assemble the `{patchwork}` 
as you would otherwise with `+ / - * &` or `patchwork::wrap_plots()`.

```{r figpatch}
img <- fig("inst/extdata/fig.png")

plt <- ggplot(mtcars) + 
  aes(mpg, cyl) + 
  geom_point() + 
  theme(plot.tag = element_text(hjust = 0, 
                                vjust = 1))

pat <- patchwork::wrap_plots(img, plt, plt, img)
pat
```

Patchwork already provides support for quick labelling of sub-plots and sub-figures
using `patchwork::plot_annotation()`.
```{r}
pat + plot_annotation(tag_levels = "A")
```

For figures which are all just images, labelling _on top_ of the image is 
sometimes desired. {patchwork} currently utilises the ggplot `tag` option 
from `ggplot2::labs(tag = ...)` but which currently [doesn't support tagging inside plot borders.](https://github.com/tidyverse/ggplot2/issues/4297). 

#### The assembled patchwork.
```{r fig.height=2, fig.width=7}
knitr::opts_chunk$set(fig.height = 2, fig.width = 7)
```


```{r fig.height=2, fig.width=7}
patchwork::wrap_plots(img, img, img, nrow = 1)
```

### The default tagging behaviour.
```{r}
patchwork::wrap_plots(img, img, img, nrow = 1) + 
  plot_annotation(tag_levels = "A")
```


### Manually Tagging
A current solution to this is the `figlab()` function which will add 
a supplied tag to the supplied fig.

```{r}
img1 <- figlab(img, "A")
img2 <- figlab(img, "(B)")
img3 <- figlab(img, "misc")

patchwork::wrap_plots(img1, img2, img3, nrow = 1)
```

A number of default positions are available, as well as support for custom `x & y` 
coordinates.

```{r}
img1 <- figlab(img, "A", pos = "topright")
img2 <- figlab(img, "(B)", pos = "bottomleft")
img3 <- figlab(img, "misc", pos = c(0.4, 0.9))

patchwork::wrap_plots(img1, img2, img3, nrow = 1)
```

## `figwrap()`
To quickly label and wrap multiple figures, use `figwrap()` 

```{r}
figwrap(list(img, img, img), "A", prefix = "(", suffix = ")")
```


```{r}
knitr::opts_chunk$set(fig.height = 5, fig.width = 7)
```

Assembling lots of figures.

```{r}
figs <- lapply(1:9, function(x) img)

figwrap(figs, nrow = 3, labelling = 1, suffix = ")")
```

## Adding specific sub-plot text.
At the end of the day, each of the figs is just a `ggplot()` object, so axis
labels can be used to add text below and above. Designs in `patchwork` can 
also be used to arrange the figures specifically.

```{r warning=FALSE}
img1 <- img1 + labs(x = "A label below the fig.")

img2 <- img2 + labs(x = "A label below the fig.") + 
  theme(axis.title.x = element_text(face = "italic"))
  

design <- "AB
           CC"

patchwork::wrap_plots(img1, img2, img3, design = design)
```

